Are We Reusing Outdated Code from Stack Overflow?

### 2017-01-22 cloneoverflow-latex/cloneoverflow.tex
substantially improved the Related Work section.

%Conference
\conferenceinfo{MSR '17}{May 20--21, 2017, Buenos Aires, Argentina}

@@

Code cloning is an activity of reusing source code by copying and pasting. It normally occurs in software development and account from 7\% to 23\% in typical software systems \cite{Bellon2007}. The benefits and drawbacks of clones are still controversial. Several authors state that clones lead to bug propagations and software maintenance issues \cite{Kamiya2002}, while some others have proofs that in some cases clones are not harmful than normal code or even beneficial \cite{Saini2016,Kapser2006}. Code cloning can also have side effects of violating software licenses. Carelessly cloning code from one project to another project with different license may cause software licensing violation \cite{German2009}. Security is also among the main concerns when code is copied from online source. A study finds that \FIXME{add this} \cite{Acar2016}.

@@

\begin{figure*}
\begin{lstlisting}
/* Code in Stack Overflow #22315734 */                      /* WritableComparator.java (2016-09-26) */
1 public int compare (byte[] b1,int s1,int l1,              1 public int compare(byte[] b1,int s1,int l1,
2                     byte[] b2,int s2,int l2) {            2                    byte[] b2,int s2,int l2) {
3   try {                                                   3   try {
4     buffer.reset(b1,s1,l1); /* parse key1 */              4     buffer.reset(b1,s1,l1); /* parse key1 */
5     key1.readFields(buffer);                              5     key1.readFields(buffer);
6     buffer.reset(b2,s2,l2); /* parse key2 */              6     buffer.reset(b2,s2,l2); /* parse key2 */
7     key2.readFields(buffer);                              7     key2.readFields(buffer);
8   } catch (IOException e) {                               8     buffer.reset(null,0,0); /* clean up reference */
9     throw new RuntimeException(e);                        9   } catch (IOException e) {
10   }                                                      10    throw new RuntimeException(e);
11   return compare(key1,key2); /* compare them */          11  }
12 }                                                        12  return compare(key1, key2); /* compare them */
                                                            13 }
\end{lstlisting}
\caption{The same code fragments, WritableComparator.java, on Stack Overflow post 22315734 and latest version in hadoop code base}
\label{fig:before-after}
\end{figure*}

@@

\section{Empirical Study}
We perform an empirical study of online code clones between Stack Overflow and 109 Java open source projects to answer the following research questions: \\ 
\textbf{RQ1 (online code clones):} \textit{To what extent  source code is cloned between Stack Overflow and open source projects?} We would like to quantitatively measure the number of online code clones between Stack Overflow and open source projects to understand the scale of the problem. \newline
%\textbf{RQ2 (flow of online code clones):} \textit{what are the directions that source code is cloned?} If clones between the two locations exist, we would like to observe in which direction the code has been copied. Is it mostly from Stack Overflow to open source projects, or the other way around, or equally both? \newline
\textbf{RQ2 (classification of online code clones):} \textit{What are the reasons of creating online code clones?} We categorise online clones into seven groups according to our clone classification scheme. %so we can differentiate and understand the motivation of cloning. 
Clones can be copied from open source projects to Stack Overflow as examples, or vice versa. Furthermore, they can be cloned from a third-party location or clones containing boiler-plate code, and code stubs generated by IDE. \newline
\textbf{RQ3 (effects of online code clones):} \textit{what are the effects derived from online code clones? can they be harmful to software development?} Is there observable problems caused by clones between Stack Overflow and open source projects?

@@

\subsubsection{Clone Candidate Filtering Using Agreement}
Usually a number of clones detected between two large-scale datasets  can be huge. In our study, there are totally 266,837,480 clone pairs reported. It is infeasible for human to manually validate all of them. One can do sampling of clones from this huge clone pair set. However, they may end up having most of them false positive clones. Therefore, we adopted an idea of clone agreement which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}. By using this agreed clone detection approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find an agreement of two clone pairs, we resort to the approach of clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair. A good-match clone pair has stronger agreement than an ok-match pair. We follow the same following definitions of good- and ok-match introduced in the original paper.

@@

\subsection{Clone detectors' parameter tuning}
We are aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies \cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}. However, considering the size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we are hindered from searching for the best configurations of the tools. Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{df}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}). The details of the two configurations are described in \Cref{t:param_tuning}. Having two clone detectors multiplied by two chosen configurations, we look for agreements in four possible pair-wise combinations: Simian$_{df}$--NiCad$_{df}$, Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.

@@

\section{Results and discussion}

We follow the experimental framework and detect clones between Stack Overflow and Qualitas corpus using the two selected clone detectors. To answer RQ1 and RQ2 together, we compute statistics of clone discovered by the tools and the true clone pairs confirmed by manual investigation. In the manual investigation process, we proposed an online clone classification scheme derived from common patterns found in online code clones. For RQ3, we look at the true positive clone pairs carefully and compare them to their latest versions. This is to see if the cloned code is still up-to-date. We also look at the license of each clone and observe a possibility of licensing violation because of cloning.
\subsection{RQ1: Online code clones}

@@

The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} configurations are presented in \Cref{tab:raw_stats}. Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 fragments. These 11 fragments trigger Simian to generate large clone clusters containing a huge number of false clones of array initialisation. Hence, they were removed from Simian's clone reports before the analysis. From \Cref{tab:raw_stats}, Simian clones cover approximately 10\% of the 144,075 Stack Overflow snippets, 1,406 reported by Simain$_{df}$ and 1,360 from Simain$_{\textrm{\textit{EvCl}}}$ respectively. NiCad$_{df}$ reports clones in 1,197 Stack Overflow code snippets, while NiCad$_{\textrm{\textit{EvCl}}}$ reports clones in a larger number of 12,884 snippets  mainly due to its relaxed configurations. In terms of number of clone pairs, Simian$_{\textrm{\textit{EvCl}}}$ and NiCad$_{\textrm{\textit{EvCl}}}$ report an enormous number of clone pairs of 59,936,722 and 206,718,663 respectively. This is expected since EvaClone configurations prefer recall \cite{Wang2013}. The average clone size of Simian$_{df}$ is 7.45 lines which is bigger than its Simian$_{\textrm{\textit{EvCl}}}$ counterpart of 4.81. Similarly, NiCad$_{df}$ has an average clone size of 9.54 lines which is bigger than 5.31 reported by NiCad$_{\textrm{\textit{EvCl}}}$. We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones. The average percentage of Stack Overflow code snippets that are cloned according to Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is 28\%, 29\%, 25\%, and 21\% accordingly.

@@

%\begin{table*}[h]
%	\centering
%	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian and NiCad}
%	\label{tab:raw_stats}
%%	\resizebox{\columnwidth}{!}{%
%	\small
%		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
%			\hline
%			\multirow{3}{*}{Statistics} 
%			& \multicolumn{3}{c|}{Simian$_{df}$} 
%			& \multicolumn{3}{c|}{Simian$_{\textrm{\textit{EvCl}}}$}
%			& \multicolumn{3}{c|}{NiCad$_{df}$} 
%			& \multicolumn{3}{c}{NiCad$_{\textrm{\textit{EvCl}}}$} \\ \cline{2-13} 
%			& \multicolumn{3}{c|}{1406 fragments} 
%			& \multicolumn{3}{c|}{1360 fragments}  
%			& \multicolumn{3}{c|}{1197 fragments} 
%			& \multicolumn{3}{c}{12884 fragments} \\ \cline{2-13}
%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
%			\hline
%			Total & 54790 & -- & -- 		& 59936722 & --	& -- 		& 127305 	& -- & -- 	& 206718663 & -- & -- \\
%			Mean & 52 & 7.45 & 28\% 		& 44104 & 4.81 & 29\% 		& 106 & 9.54 & 25\% 	& 16046 & 5.31 & 21\% \\
%			Std Dev. & 147 & 3.22 & 23\% 	& 1040483 & 1.20 & 19\% 	& 209 & 3.10 & 18\% 	& 21890 & 1.92 & 16\% \\
%			Max  & 1020 & 49.00 & 94\% 		& 38223637 & 18.00 & 89\% 	& 2100 & 39.00 & 81\% 	& 442655 & 50.00 & 93\% \\
%			Min  & 1 & 5.00 & 1\% 			& 1 & 4.00 & 2\% 			& 1 & 7.00 & 2\% 		& 1 & 3.00 & 1\% \\
%			Median  & 3 & 7.00 & 21\% 		& 24 & 5.00 & 25\% 			& 20 & 8.00 & 19\% 		& 8003 & 5.00 & 16\% \\
%			Mode  & 1 & 7.00 & 33\% 		& 1 & 4.00 & 50\% 			& 1 & 8.00 & 67\% 		& 1 & 4.00 & 33\% \\
%			\hline
%		\end{tabular} %
%%	}
%\end{table*}

%\begin{table*}
%	\centering
%	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
%	\label{t:new_and_old}
%%	\resizebox{\columnwidth}{!}{%
%	\small
%		\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
%			\hline 
%			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
%			\hline
%			antlr4 & 4.0 & 4.5.4 & 25/09/2016 & git & BSD & \\
%			apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache2.0 & \\
%			argouml & 0.34 & 0.35.4 & 11/01/2015 	& svn & Eclipse  1.0 & \\
%			artofillusion & 2.8.1 & 3.0.2 & 27/08/2016 & svn & GPL 2.0 & \\
%			aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse   1.0 & \\
%			axion & 1.0-M2 & - & 08/03/2013 & - & Proprietary (BSD/Apache-style) & \\
%			batik & 1.7 & 1.9.0 & 11/05/2016 & svn & Apache , v.2.0 & \\
%			c-jdbc & 2.0.2 & - & 16/09/2005 & - & LGPL 2.1 & \\
%			castor & 1.3.1 & 1.4.2 & 17/08/2016 & git & Apache 2.0 & \\
%			cayenne & 3.0.1 & 4.0.M4 &  26/09/2016 & git & Apache 2.0 & \\
%			checkstyle & 5.1 & 7.2  & 23/09/2016 & git & LGPL 2.1 \& Apache 2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
%			cobertura & 1.9.4.1 & 2.1.2 & 01/06/2016 & git & GPL 2.0  & \\
%			colt & 1.2.0 & - & 09/09/2014 & - & Proprietary (CERN) & Found multithreaded v. \\
%			columba & 1.4 & - & 20/04/2007 & - & Mozilla   1.1  & \\
%			commons-collections & 3.2.1 & 4.2 & 12/09/2016 & svn & Apache 2.0 & \\
%			compiere & 330 & - & - & - & GPL 2.0 & No longer OSS \\
%			db-derby & 10.6.1.0 & 10.12.1 & 13/08/2016 & svn & Apache 2.0 & \\
%			displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT  & \\
%			drawswf & 1.2.9 & - & 02/04/2013 & - & GPL 2.0 & \\
%			drjava & 20100913-r5387 & ??? & 03/09/2014 & svn & BSD  & Build to see version? \\
%			exoportal & ??? & ??? &  & git & LGPL 3.0 \& proprietary & Too many new projects \\
%			emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & - & Common   1.0 & \\
%			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & LGPL 2.0 & \\
%			fit-java & 1.1 & - & 04/06/2013 & - & GPL 2.0 & \\
%			fitlibrary & 20100806 & ??? & 29/07/2014 & git & GPL 2.0 & \\
%			freecol & 0.10.7 & 0.11.6 & 26/09/2016 & git & GPL 2.0 &  \\
%			freecs & 1.3.20100406 & - & 22/04/2013 & - & GPL 3.0 &   \\
%			freemind & 0.9.0 & 1.0.0 & 16/08/2016 & git & GPL 2.0+ &  \\
%			galleon & 2.3.0 & 2.5.6 & 29/04/2013 & - & GPL 2.0 & \\
%			ganttproject & 2.0.9 & 2.8.1 & 16/08/2016 & git & GPL 3.0 &  \\
%			geotools & 2.7-M3 & 16 & 27/09/2016 & git & LGPL 2.0 & \\
%			hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0 & \\
%			heritrix & 1.14.4 & - & 05/06/2013 & - & LGPL 2.1 & \\
%			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & LGPL 2.1+ & \\
%			hsqldb & 2.0.0 & 2.3.4 & 13/09/2016 & svn & BSD  & \\
%			htmlunit & 2.8 & 2.24 & 26/09/2016 & svn & Apache 2.0 & \\
%			ireport & 3.7.5 & - & 28/05/2014 & - & Affero LGPL 3.0 & \\
%			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero LGPL 3.0 & \\
%			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & LGPL 2.1 \& Apache Software 1.1 & \\
%			ivatagroupware & 0.11.3 & - & 27/02/2013 & - & GPL 2.0 & \\
%			jfin\_datemath & R1\_0\_1 & - & 25/04/2013 & - & GPL 2.0 & \\
%			joggplayer & 114s & - &  15/04/2013 & - & GPL 2.0 & \\
%			jag & 6.1 & 6.2 & 08/04/2013  & - & GPL 2.0 \& BSD  & BSD  is for libraries. \\
%			james & 2.2.0 & 2.3.2.1 & 14/08/2015 & - & Apache 2.0 & \\
%			jasml & 0.10 & - & 08/03/2013 & - & Apache Software  & \\
%			jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & LGPL 3.0 &  \\
%			javacc & 5.0.0 & 7.0.0 & 15/08/2016 & svn & Proprietary (Sun) & \\
%			jboss (wildfly) & 5.1.0.GA & 11.0.0.Alpha1 & 27/09/2016 & git & LGPL 2.1 & Renamed to Wildfly. \\
%			jchempaint & 3.0.1 & 3.4 & 01/09/2016 & git & LGPL 2.1+ &  \\
%			jedit & 4.3.2 & 5.3.1 & 20/09/2016 & svn & GPL 2.0 &  \\
%			jena & 2.6.3 & 3.1.1 & 16/09/2016 & git & Apache 2.0 & \\
%			jext & 5.0 & - & 18/08/2004 & - & GPL 2.0 &  \\
%			jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & LGPL 2.0 &   \\
%			jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) & \\
%			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& LGPL (derivatives) & \\
%			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & LGPL 2.1 \& Eclipse  1.0 & \\
%			jgroups & 2.10.0.GA & 4.0.0 & 26/09/2016 & git & Apache 2.0 & \\
%			jmoney & 0.4.4 & ??? & 27/12/2015 & git & GPL 2.0 &  \\
%			jparse & 0.96 & - & 29/07/2004 & - & LGPL 2.1 & \\
%			jpf & 1.5.1 & ??? & 13/01/2012 & - & Apache 2.0 & \\
%			junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 & \\
%			shiftone-jrat & 0.6 & 1-beta-1 & 17/11/2007 & svn & LGPL 2.0 &  \\
%			vuze & 4812 & 5730 & 23/09/2016 & svn & GPL 2.0 & \\
%			\hline
%		\end{tabular} %
%%	}
%\end{table*}

@@

\begin{table}[H]
	\centering
	\caption{Distribution of agreed clone pairs using Bellon's criteria for \textit{df} and \textit{EvCl} settings}
	\label{t_agreed_good_clone_pairs}
	\small
	\begin{tabular}{l|l|r|r}
		\hline
		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c}{No.~of clone pairs} \\
		\hline
		Simian & NiCad & good-match & ok-match \\
		%\hline
		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvCl}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvCl}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		\textit{df} & \textit{df} & 10 	& 9062 \\ 
		\textit{df} & \textit{EvCl} 	& 26 	& 1017 \\ 
		\textit{EvCl} 	& \textit{df} 	& 10 	& 88 \\
		\textit{EvCl} 	& \textit{EvCl} 	& 2228 & 19777 \\ 
		\hline
		\multicolumn{2}{l|}{Total} & 2274 & 29944 \\
		\hline
		\multicolumn{2}{l|}{Total (unique)} & 2261 &  29091 \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}
	\centering
	\caption{Statistics of disagreed clone pairs (Simian$_{df}$ and NiCad$_{df}$).}
	\label{tab:classification_indv_stats}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|p{2.4cm}|r|r|r}
		\hline 
		Tool & Filter & C$_{\textrm{\textit{pairs}}}$ & good/ok & remaining \\ 
		%\hline 
		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
		\hline
		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline reg.~expressions & 67570 & 2546 & 871 \\ %140 + 1482 + 926
		\hline
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-1} & 7040  & 226 & 6700 & 114 \\
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ & 229176  & 450 & 168 \\
		\hline
	\end{tabular} %
	}
\end{table}

\subsection{RQ2: Classifications of online code clones}

@@

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow #23520731 */     /* SchemaUpdate.java (2016-09-26) */
public void execute (Target target) {      public void execute(EnumSet<TargetType> targetTypes, 
  LOG.runningHbm2ddlSchemaUpdate();                        Metadata metadata, ServiceRegistry serviceRegistry) {
  Connection connection = null;              if ( targetTypes.isEmpty() ) {
  Statement stmt = null;                       LOG.debug(""Skipping SchemaExport as no targets were specified"");
  Writer outputFileWriter = null;              return;
  exceptions.clear();                        }
  try {                                      exceptions.clear();
    DatabaseMetadata meta;                   LOG.runningHbm2ddlSchemaUpdate();
    ...                                      ...
	\end{lstlisting}
	\caption{Outdated code fragment on Stack Overflow post 23520731. This code has been copied from SchemaUpdate.java and its latest version in hibernate code base contains several modifications.}
	\label{fig:hibernate_outdated_code}
\end{figure*}

@@

Data on Stack Overflow can be exploited to support developers in several ways. Seahawk is an eclipse plug-in that can search and recommend relevant code snippets from Stack Overflow \cite{Ponzanelli2013}. Similarly, Prompter, ... \cite{Ponzanelli2014}.

>>>>

%Conference
\conferenceinfo{ESEC/FSE 2017}{September 4--8, 2017, Paderborn, Germany}

@@

Code cloning is an activity of reusing source code by copying and pasting. It normally occurs in software development and account from 7\% to 23\% in typical software systems \cite{Bellon2007}. The benefits and drawbacks of clones are still controversial. Several authors state that clones lead to bug propagations and software maintenance issues \cite{Kamiya2002}, while some others have proofs that in some cases clones are not harmful than normal code or even beneficial \cite{Saini2016,Kapser2006}. Code cloning can also have side effects of violating software licenses. Carelessly cloning code from one project to another project with different license may cause software licensing violation \cite{German2009}. Security is also among the main concerns when code is copied from online source. A study by Acar et al.~shows that Stack Overflow helps developers to solve Android programming problems more quickly than other resources. However, it gives less secure code than books and the official Android documentation \cite{Acar2016}.

@@

\begin{figure*}
\begin{lstlisting}
/* Code in Stack Overflow #22315734 */                    /* WritableComparator.java (2016-09-26) */
public int compare (byte[] b1,int s1,int l1,              public int compare(byte[] b1,int s1,int l1,
                    byte[] b2,int s2,int l2) {                               byte[] b2,int s2,int l2) {
  try {                                                     try {
    buffer.reset(b1,s1,l1); /* parse key1 */                  buffer.reset(b1,s1,l1); /* parse key1 */
    key1.readFields(buffer);                                  key1.readFields(buffer);
    buffer.reset(b2,s2,l2); /* parse key2 */                  buffer.reset(b2,s2,l2); /* parse key2 */
    key2.readFields(buffer);                                  key2.readFields(buffer);
  } catch (IOException e) {                                   buffer.reset(null,0,0); /* clean up reference */
    throw new RuntimeException(e);                          } catch (IOException e) {
  }                                                           throw new RuntimeException(e);
  return compare(key1,key2); /* compare them */             }
}                                                           return compare(key1, key2); /* compare them */
                                                          }
\end{lstlisting}
\caption{The same code fragments, WritableComparator.java, on Stack Overflow post 22315734 and latest version in hadoop code base}
\label{fig:before-after}
\end{figure*}

@@

\section{Empirical Study}
We perform an empirical study of online code clones between Stack Overflow and 109 Java open source projects to answer the following research questions: \\ 
\textbf{RQ1 (online code clones):} \textit{To what extent  source code is cloned between Stack Overflow and open source projects?} We would like to quantitatively measure the number of online code clones between Stack Overflow and open source projects to understand the scale of the problem. \newline
%\textbf{RQ2 (flow of online code clones):} \textit{what are the directions that source code is cloned?} If clones between the two locations exist, we would like to observe in which direction the code has been copied. Is it mostly from Stack Overflow to open source projects, or the other way around, or equally both? \newline
\textbf{RQ2 (reasons for creating online code clones):} \textit{Why do online code clones occur?} We categorise online clones into seven groups according to our classification scheme. %so we can differentiate and understand the motivation of cloning. 
Clones can be copied from open source projects to Stack Overflow as examples, or vice versa. Furthermore, they can be cloned from a third-party location or clones containing boiler-plate code, and code stubs generated by IDE. \newline
\textbf{RQ3 (effects of online code clones):} \textit{what are the effects derived from online code clones? can they be harmful to software development?} Is there observable problems caused by clones between Stack Overflow and open source projects?

@@

\subsubsection{Prioritise Clone Candidates Using Agreement}
Usually a number of clones detected between two large-scale datasets  can be huge. In our study, there are totally 266,837,480 clone pairs reported. It is almost infeasible for human to manually validate them all. One can do a random sampling of clones. However, they may end up having most of them being false positive clones. Therefore, we adopted an idea of clone agreement which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}. By using this agreed clone detection approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find an agreement of two clone pairs, we resort to the approach of clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair. A good-match clone pair has stronger agreement than an ok-match pair. We follow the same following definitions of good- and ok-match introduced in the original paper.

@@

\subsection{Clone Detector's Parameter Tuning}
We are aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies \cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}. However, considering the size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we are hindered from searching for the best configurations of the tools. Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{df}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}). The details of the two configurations are described in \Cref{t:param_tuning}. Having two clone detectors multiplied by two chosen configurations, we look for agreements in four possible pair-wise combinations: Simian$_{df}$--NiCad$_{df}$, Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.

@@

\section{Results and Discussion}

We follow the experimental framework and detect clones between Stack Overflow and Qualitas corpus using the two selected clone detectors. To answer RQ1 and RQ2 together, we compute statistics of clone discovered by the tools and the true clone pairs confirmed by manual investigation. In the manual investigation process, we proposed an online clone classification scheme derived from common patterns found in online code clones. For RQ3, we look at the true positive clone pairs carefully and compare them to their latest versions. This is to see if the cloned code is still up-to-date. We also look at the license of each clone and observe a possibility of licensing violation because of cloning.
\subsection{RQ1: Online Code Clones}

@@

\begin{table}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) after using clone agreement}
	\label{tab:online_clone_pairs}
	\small
	\begin{tabular}{l|r}
		\hline
		Setting & No.~of clone pairs \\ 
		\hline 
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 2,261  \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}    & 29,099 \\
		\multirow{1}{*}{\textit{Simian$_{df}$}}    & 871    \\
		\multirow{1}{*}{\textit{NiCad$_{df}$}}     & 168    \\ 
		\hline
		Total                                      & 32,399 \\ 
		\hline
	\end{tabular} 
\end{table}

The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} configurations are presented in \Cref{tab:raw_stats}. Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 fragments. These 11 fragments trigger Simian to generate large clone clusters containing a huge number of false clones from array initialisation. Hence, they were removed from Simian's clone reports before the analysis. From \Cref{tab:raw_stats}, Simian clones cover approximately 10\% of the 144,075 Stack Overflow snippets, 1,406 reported by Simain$_{df}$ and 1,360 from Simain$_{\textrm{\textit{EvCl}}}$ respectively. NiCad$_{df}$ reports clones in 1,197 Stack Overflow code snippets, while NiCad$_{\textrm{\textit{EvCl}}}$ reports clones in a larger number of 12,884 snippets  mainly due to its relaxed configurations. In terms of number of clone pairs, Simian$_{\textrm{\textit{EvCl}}}$ and NiCad$_{\textrm{\textit{EvCl}}}$ report an enormous number of clone pairs of 59,936,722 and 206,718,663 respectively. This is expected since EvaClone configurations prefer recall \cite{Wang2013}. The average clone size of Simian$_{df}$ is 7.45 lines which is bigger than its Simian$_{\textrm{\textit{EvCl}}}$ counterpart of 4.81. Similarly, NiCad$_{df}$ has an average clone size of 9.54 lines which is bigger than 5.31 reported by NiCad$_{\textrm{\textit{EvCl}}}$. We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones. The average percentage of Stack Overflow code snippets that are cloned according to Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is 28\%, 29\%, 25\%, and 21\% accordingly.

@@

@@

\begin{table}[H]
	\centering
	\caption{Distribution of agreed clone pairs using Bellon's criteria for \textit{df} and \textit{EvCl} settings}
	\label{t_agreed_good_clone_pairs}
	\small
	\begin{tabular}{l|l|r|r}
		\hline
		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c}{No.~of clone pairs} \\
		\hline
		Simian          & NiCad             & good-match & ok-match \\
		\hline
		\textit{df}     & \textit{df}       & 10 	     & 9,062     \\ 
		\textit{df}     & \textit{EvCl}     & 26 	     & 1017     \\ 
		\textit{EvCl} 	& \textit{df} 	    & 10 	     & 88       \\
		\textit{EvCl} 	& \textit{EvCl}     & 2,228      & 19,777    \\ 
		\hline
		\multicolumn{2}{l|}{Total}          & 2,274      & 29,944    \\
		\hline
		\multicolumn{2}{l|}{Total (unique)} & 2,261      & 29,099    \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}
	\centering
	\caption{Statistics of disagreed clone pairs (Simian$_{df}$ and NiCad$_{df}$).}
	\label{tab:classification_indv_stats}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|p{2.4cm}|r|r|r}
		\hline 
		Tool & Filter & C$_{\textrm{\textit{pairs}}}$ & good/ok & remaining \\ 
		%\hline 
		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
		\hline
		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline reg.~expressions & 67,570 & 2,546 & 871 \\ %140 + 1482 + 926
		\hline
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-1} & 7040  & 226 & 6700 & 114 \\
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ & 229,176  & 450 & 168 \\
		\hline
	\end{tabular} %
	}
\end{table}

\subsection{RQ2: Reasons for Creating Online Code Clones}

@@

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow #23520731 */     /* SchemaUpdate.java (2016-09-26) */
public void execute (Target target) {      public void execute(EnumSet<TargetType> targetTypes, 
  LOG.runningHbm2ddlSchemaUpdate();                        Metadata metadata, ServiceRegistry serviceRegistry) {
  Connection connection = null;              if ( targetTypes.isEmpty() ) {
  Statement stmt = null;                       LOG.debug(""Skipping SchemaExport as no targets were specified"");
  Writer outputFileWriter = null;              return;
  exceptions.clear();                        }
  try {                                      exceptions.clear();
    DatabaseMetadata meta;                   LOG.runningHbm2ddlSchemaUpdate();
    ...                                      ...
	\end{lstlisting}
	\caption{Outdated code fragment on Stack Overflow post 23520731. This code has been copied from SchemaUpdate.java and its latest version in hibernate code base contains heavy modifications.}
	\label{fig:hibernate_outdated_code}
\end{figure*}

@@

Stack Overflow is a gold mine for software engineering research. Its rich and developer-driven data are valuable for software development. The data set has been put to use in several previous studies. In terms of developer-assisting tools, Seahawk is an eclipse plug-in that can search and recommend relevant code snippets from Stack Overflow \cite{Ponzanelli2013}. A follow up work, Prompter, by Ponzanelli et al.~\cite{Ponzanelli2014} is also an Eclipse plug-in for recommending relevant discussion from Stack Overflow but with improved algorithms. Several code search systems are proposed using whole or partial data from Stack Overflow \cite{Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014}. Treude et al.~try to do something \cite{Treude2016}.

Another aspect is knowledge extraction from Stack Overflow. Nasehi et al.~studied what makes a good code example by analysing answers from Stack Overflow \cite{Nasehi2012}. Studies to understand developers' behaviours on Stack Overlow include \cite{Wang2013_StackOverflow, Movshovitz-Attias2013,Rosen2016,Subramanian2013}.
A study of copy and paste behaviour has been done by Ahmed et al.~\cite{Ahmed2015}. Some studies aim to improve Stack Overflow systems \cite{Diamantopoulos2015, Wang2014, Bosu2013}.
